An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Some fixes and questions in experimental workflow

The trend concerning the parallel execution multi-population algorithms go from
earlier hardware-based implementations using transputers
\cite{gorges1990explicit}, multi-threaded \cite{merelo2019scaling}, and
multi-core systems \cite{Serrano2008,lai2019adaptive}. % many citations here - JJ 
And recently the focus has been on exploiting a higher number of processing
units by using GPUs \cite{tan2015survey,li2007efficient}, or distributed
systems; techniques used to achieve this include web-based \cite{JSON},
map-reduce \cite{fazenda2012},  grid \cite{munawar2010design,Gonzalez09},
voluntary computing \cite{MilkyWay}, and cloud computing
\cite{GValdez2015,salza2019speed,valenzuela2015implementing,FlexGP}. % many references here too - JJ 
Cloud computing has become the standard way of running
enterprise applications, not only because of the convenience of the
pay-as-you-go model or the non-existent cost of administration, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  However,  cloud computing has also been evolving, going from simply
putting in the cloud old-style monolithic applications, that is, applications
built on a single stack of services that communicate by layers, to microservices
\cite{microservices} and serverless architectures \cite{varghese2018next,
Varghese2018849} that favor the parallel and asynchronous communication of
heterogeneous resources; in the process, a new process for designing {\em cloud
native applications} has been created, with brand new methodologies and
techniques \cite{Baldini2016287}. In these architectures, services or even
functions are seen as single processing points, departing from the monolithic
and even distributed paradigms, become a loosely coupled collection of {\em
stateless functions} \cite{malawski2017serverless}, that react to events and
only come into existence while they are doing some processing. % many references more here - JJ 
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive} and they are commonly
more flexible, loosely-coupled, and scalable. % Some properies and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

@@

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in Evo\-Swarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub. Another option is to upload the image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the Fi file to specify the
type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers or downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script using the
experiment id to generate a collection of files containing all the data
generated by the experiment. The script generates these files in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper.  There is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

>>>>

The trend concerning the parallel execution multi-population algorithms go from
earlier hardware-based implementations using transputers
\cite{gorges1990explicit}, multi-threaded \cite{merelo2019scaling}, and
multi-core systems \cite{Serrano2008,lai2019adaptive}. % many citations here - JJ 
And recently the focus has been on exploiting a higher number of processing
units by using GPUs \cite{tan2015survey,li2007efficient}, or distributed
systems; techniques used to achieve this include web-based \cite{JSON},
map-reduce \cite{fazenda2012},  grid \cite{munawar2010design,Gonzalez09},
voluntary computing \cite{MilkyWay}, and cloud computing
\cite{GValdez2015,salza2019speed,valenzuela2015implementing,FlexGP}. % many references here too - JJ 
Cloud computing has become the standard way of running
enterprise applications, not only because of the convenience of the
pay-as-you-go model or the non-existent cost of administration, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  However,  cloud computing has also been evolving, going from simply
putting in the cloud old-style monolithic applications, that is, applications
built on a single stack of services that communicate by layers, to microservices
\cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} that favor the parallel and asynchronous communication of
heterogeneous resources; in the process, a new process for designing {\em cloud
native applications} has been created, with brand new methodologies and
techniques \cite{Baldini2016287}. In these architectures, services or even
functions are seen as single processing points, departing from the monolithic
and even distributed paradigms, become a loosely coupled collection of {\em
stateless functions} \cite{malawski2017serverless}, that react to events and
only come into existence while they are doing some processing. % many references more here - JJ 
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive} and they are commonly
more flexible, loosely-coupled, and scalable. % Some properies and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

@@

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in Evo\-Swarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the Fi file
% Fi file? - JJ+
to specify the
type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers, downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the
experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.
